Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-23 draft_report.qmd
Add imd cluster details

>>>>

patientweighted_practice_imd |>
  mutate(gp_imd_quantile = case_when(gp_imd_decile<=2 ~ 1,
                                     gp_imd_decile==3 ~2,
                                     gp_imd_decile==4 ~2,
                                     gp_imd_decile==5 ~3,
                                     gp_imd_decile==6 ~3,
                                     gp_imd_decile==7 ~4,
                                     gp_imd_decile==8 ~4,
                                     gp_imd_decile>=9 ~5,
                                     .default = 0
  ))|>
  group_by(gp_imd_quantile,cluster)|>
  summarise(patients=sum(patients))|>
  gt()
```
